Crystals

### 2017-01-31 doc/ms.tex
Background figure
Use \x throughout

The background component is assumed to be piecewise linear
{\todo between $\x=x_{\rm min}$ and $\x=10$, between $\x=10$ and $\x=40$,
and between $\x=40$ and $\x=\x_{\rm max}$}.
We parameterise the background component using
five parameters. Firstly, there is a mean level $b$, which sets the
typical amplitude of the background component. There are also four parameters
$n_1, ..., n_4$, which set the positions of four control points:
\begin{align}
\left(\x_{\rm min}, be^{n_1}\right) \nonumber\\
\left(10, be^{n_2}\right) \nonumber\\
\left(40, be^{n_3}\right) \nonumber\\
\left(\x_{\rm max}, be^{n_4}\right) \nonumber
\end{align}
The value of the background component at any other point is found by
linear interpolation.

@@

\hline
{\em Parameters}& &\\
$\sigma_0$ &    Constant noise level  &   $\ln(\sigma_0) \sim \textnormal{Laplace}(0,5)$\\
$\sigma_1$ &    Noise proportionality   &  $\ln(\sigma_1) \sim \textnormal{Laplace}(0,5)$ \\
$\nu$     &   Shape parameter for residuals   &   LogUniform$(1, 1000)$\\
$b$       & Mean background level       & Laplace$(0, 5)$\\
$\{n_1, ..., n_4\}$  & Background deviations & iid Normal$(0,1)$\\
\hline
{\em Data}&&\\
\hline
$\{y_1, y_2, ..., y_n\}$  &   Measurements    & Student $t(f(x_i; \params), ,\nu)$\\
\hline
{\em Prior information}&&\\
\hline
$n$ & Number of measurements & given\\
$\{x_1, x_2, ..., x_n\}$  & $x$-values of measurements & given \\
\hline
\end{tabular}
\caption{\label{tab:priors}}
\end{table}

@@

The shape of the model function $f(x)$ is therefore
\begin{align}
f(x) &= f_{\rm bg}(x) + f_{\rm wide}(x) + f_{\rm narrow}(x)
\end{align}
and the crystallinity is
\begin{align}
C &= \frac{\int f_{\rm wide}(x) \, dx}
          {\int f_{\rm wide}(x) \, dx + \int f_{\rm narrow}(x) \, dx}
\end{align}

>>>>

The background component is assumed to be piecewise linear
{\todo between $\x=\x_{\rm min}$ and $\x=10$, between $\x=10$ and $\x=40$,
and between $\x=40$ and $\x=\x_{\rm max}$}.
We parameterise the background component using
five parameters. Firstly, there is a mean level $b$, which sets the
typical amplitude of the background component. There are also four parameters
$n_1, ..., n_4$, which set the positions of four control points:
\begin{align}
\left(\x_{\rm min}, be^{n_1}\right) \nonumber\\
\left(10, be^{n_2}\right) \nonumber\\
\left(40, be^{n_3}\right) \nonumber\\
\left(\x_{\rm max}, be^{n_4}\right) \nonumber
\end{align}
The value of the background component at any other point is found by
linear interpolation. Figure~\ref{fig:background} shows three example
background curves generated from this parameterisation, with typical
values of the parameters.

\begin{figure}
\centering
\includegraphics[width=0.7\textwidth]{figures/background.pdf}
\caption{\label{fig:background}}
\end{figure}

@@

\hline
{\em Parameters}& &\\
$\sigma_0$ &    Constant noise level  &   $\ln(\sigma_0) \sim \textnormal{Laplace}(0,5)$\\
$\sigma_1$ &    Noise proportionality   &  $\ln(\sigma_1) \sim \textnormal{Laplace}(0,5)$ \\
$\nu$     &   Shape parameter for residuals   &   LogUniform$(1, 1000)$\\
$b$       & Mean background level       & Laplace$(0, 5)$\\
$\{n_1, ..., n_4\}$  & Background deviations & iid Normal$(0,1)$\\
\hline
{\em Data}&&\\
\hline
$\{y_1, y_2, ..., y_n\}$  &   Measurements    & Student $t(f(x_i; \params), ,\nu)$\\
\hline
{\em Prior information}&&\\
\hline
$n$ & Number of measurements & given\\
$\{\x_1, \x_2, ..., \x_n\}$  & $\x$-values of measurements & given \\
\hline
\end{tabular}
\caption{\label{tab:priors}}
\end{table}

@@

The shape of the model function $f(x)$ is therefore
\begin{align}
f(\x) &= f_{\rm bg}(\x) + f_{\rm wide}(\x) + f_{\rm narrow}(\x)
\end{align}
and the crystallinity is defined as the proportion of the area in the
wide and narrow components which is accounted for by the wide component:
\begin{align}
C &= \frac{\int f_{\rm wide}(\x) \, d\x}
          {\int f_{\rm wide}(\x) \, d\x + \int f_{\rm narrow}(\x) \, d\x}
\end{align}
